Section Rings of $\bq$-divisors on minimal rational surfaces

### 2017-11-13 surfaces-write-up/surface-paper.tex
fixed 26

\begin{rem}
\label{rem:proj-grobner}
	In the case that $D = \alpha_0 D_0$ is supported on a single
	hypersurface, the relations in Theorem ~\ref{thm:proj-one-point}
	form a reduced Gr\"{o}bner basis with respect to the ordering
	given in Definition~\ref{defn:vec-order}.
\end{rem}

>>>>

\begin{rem}
\label{rem:proj-grobner}
	In the case that $D = \alpha_0 D_0$ is supported on a single
	hypersurface and $D' = 0$, the relations in Theorem ~\ref{thm:proj-one-point}
	form a reduced Gr\"{o}bner basis with respect to the ordering
	given in Definition~\ref{defn:vec-order}.
\end{rem}
